Figures

### 2020-02-26 figures/02_depth_model.Rmd
add model metrics table

@@

ggplot(data = dt) + 
  geom_density(aes(x = resid, fill = shape_class)) +
  geom_vline(aes(xintercept = 0)) +
  facet_wrap(~ model)

ggplot(data = dt) + 
  geom_density(aes(x = resid, fill = reservoir_class)) +
  geom_vline(aes(xintercept = 0)) +
  facet_wrap(~ model)
```

>>>>

```{r depth_model_metrics}
dt_metrics <- readRDS("../data/01_depth_model/depth_grid_metrics.rds")
jsta::pdf_table(dt_metrics, "../tables/depth_model_metrics-1.pdf")
```

@@

ggplot(data = dt) + 
  geom_density(aes(x = resid, fill = shape_class)) +
  geom_vline(aes(xintercept = 0)) +
  facet_wrap(~ model) + 
    theme(legend.position = "none",
        plot.margin = unit(c(1.5,1.5,0.2,0.2), "cm"))
grid::grid.text(unit(0.93, "npc"), 0.32, 
                label = 'proxy slope', rot = 270) # bottom right
grid::grid.text(unit(0.93, "npc"), 0.65, 
                label = 'true slope', rot = 270) # top right
grid::grid.text(unit(0.7, "npc"), 0.89, 
                label = 'proxy distance') # right
grid::grid.text(unit(0.3, "npc"), 0.89, 
                label = 'true distance') # left

ggplot(data = dt) + 
  geom_density(aes(x = resid, fill = reservoir_class)) +
  geom_vline(aes(xintercept = 0)) +
  facet_wrap(~ model) +
  theme(legend.position = "none",
        plot.margin = unit(c(1.5,1.5,0.2,0.2), "cm"))
grid::grid.text(unit(0.93, "npc"), 0.32, 
                label = 'proxy slope', rot = 270) # bottom right
grid::grid.text(unit(0.93, "npc"), 0.65, 
                label = 'true slope', rot = 270) # top right
grid::grid.text(unit(0.7, "npc"), 0.89, 
                label = 'proxy distance') # right
grid::grid.text(unit(0.3, "npc"), 0.89, 
                label = 'true distance') # left
```

### 2020-02-26 manuscript/figures.Rmd
create bathy specific predictor table
add model metrics table

### predictor summary table

### variable importance for true slopes and distances (5)

### model metrics grid (table)

>>>>

```{r metric_correlations, fig.cap = "metric correlations", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/metric_correlations-1.pdf")
```

```{r depth_model_metrics, fig.cap = "depth model metrics", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../tables/depth_model_metrics-1.pdf")
```
